Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-18 ltx/data_paper/DataPaper.tex
correction to analytic gamma width
minor correction to disturbance support

From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required. Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small. Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively. If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required. Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving 

@@

 \sigma_d^2=\sigma_{mm\gamma}^2-4\sigma_m^2.

>>>>

From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required. Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small. Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively. If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required. Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_{\gamma}$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving 

@@

 \sigma_{\gamma}^2=\sigma_{mm\gamma}^2-2\sigma_m^2.
